He-Man: A domain-specific language for lightweight concurrency

### 2012-03-10 paper/paper.tex
Added citations; rewrote abstract.

\begin{abstract}
% XXX: better abstract;
% and where should we put the code link?

We present He-Man \cite{HeMan}, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/he-man}.
\end{abstract}

\section{Introduction}

@@

@@

\bibliography{citations}{}
\bibliographystyle{abbrvnat}

>>>>

\begin{abstract}
The event-driven model is the gold standard for highly concurrent network
application programming; while threaded code is easier to write and reason
about, it is considerably less scalable.

We observe that these paradigms are not only interchangeable, but primarily
confined to an application's core control flow; we propose a hybrid model in
which programmers express this core logic at a high level of abstraction, yet
are free to implement the remainder of the application at a low level.

This paper describes the design and Haskell implementation of He-Man, a domain
specific language for network application programming which presents a
sequential thread-like abstraction, but compiles to performant event-driven C
code. Our implementation is available at
\url{https://github.com/msullivan/he-man}.
%\cite{HeMan}
\end{abstract}

\section{Introduction}
building scalable concurrent network applications. The
language presents a

presents difficult concurrency challenges 
implementation challenge to developers
supporting many simultaneous clients
although memory and bandwidth is plentiful
difficult to design applications
to take full advantage of these resources.
threads inefficient (scheduling)
event loops (hard to write)

\cite{LauerNeedham},

in a natural, straight-line manner while
still producing efficient event loop-based code.

He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
, embedded, domain specific language in Haskell for
building

@@

\cite{*}

@@

\pagebreak
\bibliography{citations}{}
\bibliographystyle{abbrvnat}
